Katana: Towards Patching as a Part of the ELF Toolchain

### 2010-03-18 paper1/hotpatch/redundancy.tex
slight expansion to redundancy argument

>>>>

It should be noted that the last two items apply even for virtualized
redundant systems, which often do not have the traditional overhead of
redundant hardware.  We do not claim that redundancy does not have its
place, but redundancy does not provide the easy, ubiquitous solution to
high-availability stateful applications which we hope to provide
through patching

% LocalWords:  stateful virtualized
